%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer, YouTube Channel Memberships} % Job title
    {Google} % Organization
    {Zurich, Switzerland} % Location
    {Jul. 18 - Present (1 year, 5 months)} % Date(s)
    {
      \begin{cvitems}
        \item {Subscription based, user supported YouTube alternative monetization (C++, Spanner, PubSub, Stubby). Projects: iOS payment support, optimizing channel members retrieval latency (100x for large channels), pricing levels.}
        \item {20\% project: Renaming of symbols in object files (ELF, Mach-O, PE/COFF) in Rust for Mundane cryptographic library (\url{https://github.com/google/mundane}).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, core platform} % Job title
    {Tink} % Organization
    {Stockholm, Sweden} % Location
    {Oct. 2016 - Jun. 2018 (1 year, 8 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Core transaction processing platform development (Java and Go, Cassandra, MySQL, Kafka, ZooKeeper, Elasticsearch, AWS, SaltStack provisioning, Terraform-defined declarative infrastructure). Projects: up/down scaling of transaction processing, driving movement towards microservices, continues delivery pipeline, improving transaction processing performance, advocating for testing, working with infrastructure closely.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer, infrastructure services} % Job title
    {Playtika} % Organization
    {Kyiv, Ukraine} % Location
    {Mar. 2016 - Oct. 2016 (8 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Service for messages delivery via WebSockets to the end users (Spring Boot, Apache Kafka, Couchbase).}
        \item {Facebook ad audiences management service: in memory processing of large amounts of data (gigabytes) and integration with Facebook Marketing API (Spring Boot, HDFS, Apache Kafka.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, movie platform} % Job title
    {Yandex} % Organization
    {Kyiv, Ukraine} % Location
    {Apr. 2014 - Mar. 2016 (2 years)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Backend development for integrating kinopoisk.ru (movie catalogue website) with Yandex services. Working on high load (order of 10K QPS) system based on Java 8, Spring Framework, Jetty, MongoDB and MySQL. Designing (public and internal) REST APIs. Working on authentication and authorization. Load testing, performance optimization, JVM profiling. Facilitating team TDD adoption. Participating in software development best practices promotion and implementation as a team. Mentoring of new project members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer, State Street Bank} % Job title
    {DIO-Soft} % Organization
    {Kyiv, Ukraine} % Location
    {Nov. 2013 - Mar. 2014 (5 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of a backend for financial data monitoring service (Restlet Framework, Spring DI, JAXB, Sybase, SQL, JDBC, Java concurrency, TDD, JUnit, Mockito, integration testing).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer, system integration} % Job title
    {NetCracker} % Organization
    {Kyiv, Ukraine} % Location
    {Mar. 2013 - Oct. 2013 (8 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Client integration projects (Java, SOAP web services, PL/SQL, JSP, JavaScript).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern Java Developer} % Job title
    {DataArt} % Organization
    {Kyiv, Ukraine} % Location
    {Jun. 2012 - Aug. 2012 (3 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {JEE, SQL, Spring Framework, Servlets, JSP.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
